---
title: Emissions package and function description 
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Emissions

<!-- badges: start -->
<!-- badges: end -->

The goal of the `Emissions` package is to include tools to determine the amount of carbon dioxide emitted per km distance for various transportation methods. Currently, petrol and diesel cars are supported in this package via teh `co2emssion` function. 

## Installation

You can install the development version of Emissions from [GitHub](https://github.com/) with:

``` {r}
# install.packages("devtools")
devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-wettengm/Emissions", ref = "0.2.0")
```

## Example

This is a basic example which shows you how to use the `co2emisson` function within the package:

```{r example}
library(Emissions)
# Comparing CO2 emissions between petrol and diesel cars with same mpg (US gallons)
co2emission(33, petrol = TRUE)
co2emission(33, petrol = FALSE)
```

You can also have a vector of cars' mpg as input for the function. As long as the cars are all the same fuel type.
```{r}
list <- c(22,33,44)
co2emission(list, petrol = TRUE)
```